(tentative) Rotational Spectral Unmixing of Exoplanets

### 2016-11-13 paper/main.tex
spider graph
add plots showing bestfit with regularization term

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \begin{center}
\includegraphics[width=0.9\hsize]{PCA_V_jn.pdf}
    \end{center}
    \caption{Principal Components. }
\label{fig:PCs}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[bt]
    \begin{center}
%\includegraphics[width=\hsize]{PCA_projected.pdf}
\includegraphics[width=0.9\hsize]{mockdata_quadrature_PCplane.pdf}
    \end{center}
    \caption{Colors of 3 surface types and the light curves projected to the plane of 1st and 2nd principal components. }
\label{fig:shrinkwrap}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!bpth]
    \begin{center}
\includegraphics[width=\hsize]{xmed_std_reglong_l1e-2.pdf}
%\includegraphics[width=\hsize]{xmed_std_reglong_l1e-4.pdf}
    \end{center}
    \caption{Regularization in terms of longitude. Upper: $\sigma = 0.01$. Lower: $\sigma = 0.0001$. \memoYF{But the MC chains do not converge after 5000 steps!}}

\label{fig:shrinkwrap}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Questions}

\begin{itemize}
\item Is this a right usage of Gaussian Process?
\item
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[th]
    \begin{center}
\includegraphics[width=0.9\hsize]{PCA_V_jn.pdf}
    \end{center}
    \caption{Principal Components. }
\label{fig:PCs}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[bht]
    \begin{center}
%\includegraphics[width=\hsize]{PCA_projected.pdf}
\includegraphics[width=\hsize]{mockdata_quadrature_PCplane.pdf}
    \end{center}
    \caption{Colors of 3 surface types and the light curves projected to the plane of 1st and 2nd principal components. }
\label{fig:shrinkwrap}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{[NEW] Effect of Regularization Term}
\label{ss:shrinkwrap}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%
\begin{eqnarray}
\mathcal{P}_{\fast} &=& \prod _k \left[ \frac{1}{(\sqrt{ 2 \pi })^{I} \sqrt{| \tilde \Sigma |} } \right. \\
&& \left. \times \exp \left\{ - \sum _{i,\,i'} (\fast ^{T})_{ki} \tilde \Sigma_{ii'} ^{-1} \fast_{i'k} \right\} \right] \\
\tilde \Sigma _{ii'} (\lambda,  \Delta_t ) &=& \exp \left( - \frac{|t_i- t_i'|^2}{2 \Delta_t^2} \right)
\end{eqnarray}
%%%

%%%
\begin{eqnarray}
- \log \mathcal{P}_{\fast} &\propto & \frac{1}{2} | \tilde \Sigma | + \mathcal{F}(\lambda, \Delta_t; f) \\
\mathcal{F}(\lambda, \Delta_t; f)&\equiv & \sum _k \sum_{i,\,i'} (\fast ^{T})_{ki} \tilde \Sigma_{ii'} ^{-1} \fast_{i'k}
\end{eqnarray}
%%%

...I think $\fast $ here should be zero mean for each $k$. 
%%%
\begin{equation}
\fast_{ik} \rightarrow ( \fast_{ik} - \fast^{(ave)}_k )
\end{equation}
%%%
In the following figures, the vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{F}^{\ast } (\Delta_t; f) = \lambda ^2 \mathcal{F}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b]
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l90deg_2013.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l90deg_2017.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l90deg_2019.pdf}
    \end{center}
    \end{minipage}    
    \caption{The difference between the three panels is just the seed for \url{np.randam.uniform}}
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b]
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l120deg_2013.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l120deg_2017.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_regf_PCplane_l120deg_2019.pdf}
    \end{center}
    \end{minipage}
    \caption{The difference between the three panels is just the seed for \url{np.randam.uniform}}
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b]
    \begin{minipage}{0.5\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_l120deg_2013_X_albd_jk_best.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.5\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_l120deg_2013_X_area_ik_best.pdf}
    \end{center}
    \end{minipage}
    \caption{Solution with smallest regularization term. }
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
    \begin{center}
\includegraphics[width=\hsize]{xmed_std_reglong_l1e-2.pdf}
%\includegraphics[width=\hsize]{xmed_std_reglong_l1e-4.pdf}
    \end{center}
    \caption{Regularization in terms of longitude. Upper: $\sigma = 0.01$. Lower: $\sigma = 0.0001$. \memoYF{But the MC chains do not converge after 5000 steps!}}
\label{fig:xmed_std_reglong_l1e-2}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
    \begin{center}
\includegraphics[width=\hsize]{reglong_l1e-2_trace0.png}
\includegraphics[width=\hsize]{reglong_l1e-2_trace8.png}
\includegraphics[width=\hsize]{reglong_l1e-2_trace13.png}
    \end{center}
    \caption{Examples of MC chains in estimating $\{ f,\,s\}$ with $\lambda = 0.01$, corresponding to Figure \ref{fig:xmed_std_reglong_l1e-2}. }
\label{fig:shrinkwrap}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure*}[!htbp]
%    \begin{center}
%\includegraphics[width=\hsize]{xmed_std_reglong_s1e-4.pdf}
%    \end{center}
%    \caption{Result of estimation for $\{ f,\,s\}$ with $\lambda = 0.0001$. \memoYF{MC chains do not fully converge in 5000 steps.}}
%\label{fig:shrinkwrap}
%\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure*}[!htbp]
%    \begin{center}
%\includegraphics[width=\hsize]{xmed_std_time.pdf}
%\includegraphics[width=\hsize]{xmed_std_longitude.pdf}
%    \end{center}
%    \caption{Left: result of estimation for $\{ \fast,\,s\}$. Right: result of estimation for $\{ f,\,s\}$}
%\label{fig:shrinkwrap}
%\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
